---
title: "Estimating class coverage distribution under standard conformal inference"
output:
  pdf_document: default
  html_notebook: default
---
```{r}
library(deconvolveR)
library(tidyverse)
```

# Using real data

```{r}
support_pts <- seq(from = 0.01, to = 0.99, by = 0.01)
X <- read.csv("data/standard_conformal_class_coverage.csv", header=FALSE)
observed_class_cov <- X[,2] / X[,1]
result <- deconv(tau = support_pts, X = X, family = 'Binomial')

g <- result$stats[, "g"]
ggplot() +
   geom_histogram(mapping = aes(x = observed_class_cov, y = ..count../sum(..count..)), color = "blue", fill = "blue", bins = 70, alpha = 0.5) +
   geom_line(mapping = aes(x = support_pts, y = g), color = "black") +
   labs(title = "Observed class coverage (blue) and est. distr. of true class coverage (black)",
        x = "Class coverage", 
        y = "Frequency") 

```
Compute cdf of g
```{r}
G <- cumsum(g)
ggplot() +
  geom_line(aes(x = support_pts, y = G)) +
  labs(title = "CDF of estimated class coverage distribution",
        x = "Class coverage", 
        y = "cdf")  +
  lims(y=c(0,.05))

```
# Sanity checks using simulated data

To determine how well `deconvolveR` is able to recover the true prior distribution, we do the following:
  1. Choose a prior distribution $g^*$.
  2. Sample $\theta_i \sim g^*$. Then sample an "observed class coverage" (more accurately, the number of correctly predicted instances) for class $i$ from $Binom(n_i, \theta_i)$. Repeat this for all 1000 classes
  3. Feed these simulated "observed class coverages" into `deconv` using the same settings we previously used. Compare the estimated $g$ to the ground-truth $g^*$ that we chose in Step 1. 
  4. Repeat Steps 2-3 many times.
  
## Test 1
One of the "easiest" possible tests for `deconv` to pass is if we let $g^*$ be the distribution we estimated from the real data, so we will start with this


```{r}
g_star <- g
num_classes <- 1000
class_cts <- X[,1]

# Initialize array of zeros
sim_num_covered <- numeric(num_classes)

for (i in 1:num_classes) {
  theta_i <- sample(support_pts, size = 1, prob=g_star) 
  sim_num_covered[i] <- rbinom(n = 1, size = class_cts[i], prob = theta_i)
}

sim_obs_class_cov <- sim_num_covered / class_cts

data <- cbind(class_cts, sim_num_covered)
result <- deconv(tau = support_pts, X = data, family = 'Binomial')
```


```{r}
g <- result$stats[, "g"]
ggplot() +
   geom_histogram(mapping = aes(x = sim_obs_class_cov, y = ..count../sum(..count..)), color = "blue", fill = "blue", bins = 70, alpha = 0.5) +
   geom_line(mapping = aes(x = support_pts, y = g), color = "black") + # Estimated distribution
   geom_line(mapping = aes(x = support_pts, y = g_star), color = "green") + # True distribution
   labs(title = "Observed class coverage (blue) and est. distr. of true class coverage (black)",
        x = "Class coverage", 
        y = "Frequency") 
```

```{r}
G <- cumsum(g)
G_star <- cumsum(g_star)
ggplot() +
  geom_line(aes(x = support_pts, y = G, color = "Estimated cdf"), alpha=0.4) +
  geom_line(aes(x = support_pts, y = G_star, color = "True cdf")) +
  labs(title = "CDF of estimated class coverage distribution",
        x = "Class coverage", 
        y = "cdf")  +
  lims(y=c(0,.05))

```

Now we make a plot with many estimated cdfs (each from a different simulated dataset)

```{r}
num_trials <- 50
df <- matrix(0, nrow = length(g_star), ncol = num_trials)
for (j in seq_len(num_trials)) {
  
  # Simulate
  # Initialize array of zeros
  sim_num_covered <- numeric(num_classes)
  
  for (i in 1:num_classes) {
    theta_i <- sample(support_pts, size = 1, prob=g_star) 
    sim_num_covered[i] <- rbinom(n = 1, size = class_cts[i], prob = theta_i)
  }
  
  sim_obs_class_cov <- sim_num_covered / class_cts
  
  data <- cbind(class_cts, sim_num_covered)
  result <- deconv(tau = support_pts, X = data, family = 'Binomial')
  g <- result$stats[, "g"]
  
  G <- cumsum(g) # Compute cdf
  df[,j] <- G
}
df <- data.frame(df)
df <- cbind(support = support_pts, df)

df <- df %>% pivot_longer(cols = "X1":paste0("X", num_trials))
# df
```


```{r}
G_star = cumsum(g_star)
df2 <- data.frame(support_pts, G_star) # DataFrame containing true distribution 

support_pts
df %>% ggplot(mapping = aes(x = support, y = value, color=name)) + 
  geom_line(alpha=0.3) +
  geom_line(data = df2, mapping = aes(x=support_pts, y=G_star), color = "black", size=1.5) + 
  theme(legend.position = "none") + # Remove legend 
  labs(title = "Estimated cdf (colored lines) and true cdf (black line)",
        x = "Class coverage", 
        y = "cdf")  +
  ylim(c(0, .1)) # Zoom in
```
We observe that the distributions obtained using the deconvolution procedure (colored lines) have heavier tails than the true distribution (black line). However, once we get past the ~3%-quantile, the estimated distributions match the true distribution pretty closely. 